---
title: "MA710 - New York Times Articles"
author: "Xiang Li, Xue Zhou"
date: "8 Apri 2017"
output: html_document
---


# Table of Contents
* 1.[Introduction](#Introduction)
* 2.[Dataset Creation](#2)
* 3.[Load the dataset](#3)
* 4.[Base investigation](#investi0)
  * 4.1 [Data Preparation: Parameters, Value and Reasons](#4.1)
  * 4.2 [Cluster Generation](#4.2)
  * 4.3 [Cluster Evaluation](#4.3)
    * 4.3.1 [Cluster Counts](#4.3.1)
    * 4.3.2 [Numerical Evaluation with Metrics](#4.3.2)
      * 4.3.2.1 [Numerical Evaluation: Silhouette Width](#4.3.2.1)
      * 4.3.2.2 [Numerical Evaluation: Dunn Index](#4.3.2.2)
      * 4.3.2.3 [Numerical Evaluation:Connectivity](#4.3.2.3)
    * 4.3.3 [Subjective Evaluation (terms and documents in each cluster)]((#4.3.2.3))
      * 4.3.3.1 [Subjective Evaluation: Common Words]((#4.3.3.1)
      * 4.3.3.2 [Subjective Evaluation: Evaluation: Check Documents](#4.3.3.2)
  * 4.4 [Conclusion for This Iteration](#4.4)

* 5.[Investigation -iteration 2](#investi1)
* 6.[Investigation -iteration 3](#investi2)
* 7.[Conclusion](#conclusion)


```{r setup, include=FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE)

```


The following R file contains the related functions we used in this report. 
```{r echo=FALSE, message=FALSE, warning=FALSE}
source(file="~/Desktop/project3/20170321_TextMining_functions.R")
```

[The text in square brackets are my notes to you. 
 Please remove them from your draft or final report.]


# Table of Contents
* 1.[Introduction](#Introduction)
* 2.[Association Rule Analysis](#AR)
  * 2.1 [Goal](#AR_goal)
  * 2.2 [Data Preparation](#AR_dp)
  * 2.3 [Objective](#AR_objective)
  * 2.4 [Association Rule Analysis - Median earnings six years after entry](#AR_md6)
  * 2.5 [Conclusions -  Association Rule Analysis for Median earnings six years after entry](#2.5)
  * 2.6 [Association Rule Analysis - Predominant Degree](#2.6)
  * 2.7 [Conclusions -  Association Rule Analysis for Predominant Degree](#2.7)
* 3.[Cluster Analysis](#3)
  * 3.1 [Goal](#3.1)
  * 3.2 [Data Preparation](#3.2)
  * 3.3 [Objective](#3.3)
  * 3.4 [Cluster Analysis - K means](#3.4)
  * 3.5 [Cluster Analysis - PAM](#3.5)
  * 3.6 [Cluster Analysis - Hierarchical](#3.6)
  * 3.7 [Cluster Validation and Comparison](#3.7)
  * 3.8 [Interpretation of 3-cluster hierarchical solution](#3.8)
  * 3.9 [Findings and Conclusion](#3.9)
* 4 [Future Study](#4)

# 1 Introduction<a id="Introduction"></a>

[Provide background for and an introduction to the dataset.
  Describe your intended analysis and goals.]
  
# 2 Create the dataset<a id="2"></a>

[Do not run this each time you recreate your report.
 Make sure you break this into smaller code blocks and explain each.]
 
 
```{r eval=FALSE}
library(cluster)
library(RCurl)
library(RJSONIO)
library(rlist)
library(stringr)
library(dplyr)
library(magrittr)
library(RTextTools)
library(ngram)
library(wordcloud)


options(dplyr.width=Inf)
articlesearch.key = "28fdd9ef177b47f1802f26d59d81d0a9"
get.nyt.hits(query.string="technology",     # OPTION
             begin.date="20160101",    # OPTION
             end.date  ="20170107")    # OPTION
article.df = get.nyt.articles(pages = -1, 
                              query.string = "technology",
                              begin.date   = "20160101",
                              end.date     = "20170107") 
save(article.df, 
     file="~/Desktop/project3/article.df.RData")


```

# 3 Load the dataset<a id="3"></a>


[This is run every time you knit your report.]
```{r}
load(file="~/Desktop/project3/article.df.RData")

glimpse(article.df)
```
  
# 4. Base Investigation<a id="investi0"></a>

## 4.1 Data Preparation: Parameters, Value and Reasons  
[Start with a basic set of options, and explain why you chose them in the following table.]

[Do not change the first two lines (27 and 28) of the table. 
They define the columns and the headers.]

Parameter | Value | Reason
--------- | ----- | ------
Query term | "dance" | Interested in modern dance.
Begin date | 1 Jan 2017 | Interested in Jan 2017 articles.
End date   | 31 Jan 2017 | Interested in Jan 2017 articles.
Field      | `snippet` | 
Stemming   | Yes/No | 
N-grams    | 1, |
Stopwords  | "english"/"SMART" |
Stopwords  | "dance" | This is the search term.
Weighting  | binary, TF-IDF, term frequency | 
Threshold  | 2 |
Algorithm  | k-means | 
`k`        | 10 |


## 4.2 Cluster Generation
[Create your clusters here. Succinctly explain your code.] 

```{r eval=TRUE}
docs = article.df$snippet 
docs.clean = clean.documents(docs)
docs.sns = 
  modify.words(
    docs.clean,  
    stem.words=FALSE,  # OPTION: TRUE or FALSE
    ngram.vector=1:2, # OPTION: n-gram lengths
    stop.words=       # OPTION: stop words
      c(stopwords(kind="english")  
        # OPTION: "SMART" or "english" 
        # OPTION: additional stop words
      )
  )
doc.matrix <- 
  create_matrix(docs.sns, 
                language="english",      # Do not change
                stemWords=FALSE,         # Do not change
                removePunctuation=FALSE, # Do not change
                weighting=tm::weightTf   # OPTION: weighting (see below)
  )
dtm = as.matrix(doc.matrix) 
dtm=reduce.dtm(dtm,freq.threshold=2) 
k = 3
cluster = kmeans(dtm,k)$cluster
```

## 4.3 Cluster Evaluation
### 4.3.1 Cluster Counts 

The table below indicates the number of articles that are contained in each cluster. 
```{r echo=FALSE}
as.data.frame(table(cluster))
#  17  45   2   9   2  60 839  27   5   4 
```
[Interpret the information from the table. 
 Indicate which clusters are large enough to investigate further.
 Explain your reasoning.]

### 4.3.2 Numerical Evaluation with Metrics
  #### 4.3.2.1 Numerical Evaluation: Silhouette Width
  #### 4.3.2.2 Numerical Evaluation: Dunn Index
  #### 4.3.2.3 Numerical Evaluation:Connectivity

### 4.3.3 Subjective Evaluation (Terms, Documents in each cluster)
#### 4.3.3.1 Subjective Evaluation: Common Words
[Use the `TopWords` and/or `check.clusters` function to check for common words in 
 each cluster which in the previous section you chose to investigate further. 
 For each cluster indicate which words (if any) occur often enough
 to indicate a potential subject of the documents in the cluster.Indicate which clusters seem to  have a potential subject and should be investigated further.]


```{r echo=FALSE, warning=FALSE}
check.clusters(cluster, 5) 
```

```{r echo=FALSE, warning=FALSE}
# The `TopWords` function displays the documents 
# in the cluster whose number is specified with 
# third parameter
TopWords(dtm, cluster, 1) 
```

[Explain whether the documents of this cluster have a common 
 subject and describe this subject. ]

[Explain whether the documents of this cluster have a common 
 subject and describe this subject. ]


#### 4.3.3.2 Subjective Evaluation: Evaluation: Check Documents  

[Use the `view.cluster` function to read the documents in each cluster 
 which you decided in the previous section should be investigated further.
 Look for a single subject common to all or most documents in the cluster.
 For each cluster indicate whether all or most of the documents in the 
 cluster share a common subject.]
 
```{r echo=FALSE}
view.cluster(1)
```

 
## 4.4 Conclusion for this Iteration

[From your evaluation, decide which parameter you will change for the next investigation.]



# 5.Investigation -iteration 2<a id="investi1"></a>

[Describe the option you will change from your previous investigation and why you chose it.
 Modify the following table to indicate the parameter choices you made for this investigation.
 Include the reasons you made these choices. If you did not change a parameter then simply
 copy the line from the previous table.]

Parameter | Value | Reason
--------- | ----- | ------
Query term | "dance" | Interested in modern dance.
Begin date | 1 Jan 2015 | Interested in 2015 articles.
End date   | 31 Dec 2015 | Interested in 2015 articles.
Field      | `snippet` | 
Stemming   | Yes/No | 
N-grams    | 1, 2 |
Stopwords  | "english"/"SMART" |
Stopwords  | "dance" | This is the search term.
Weighting  | binary | 
Threshold  | 2 |
`k`        | 10 |

[Evaluate the clusters you create.]

[From your evaluation, decide which parameter you will change for the next investigation.]

# 6. Investigation -iteration 3<a id="investi2"></a>

[Repeat this process until you are satisfied that you have found good clusters and until you are satisfied that you have tried enough options.]
  
# 7. Conclusion<a id="conclusion"></a>

[Describe the final modifications used to create your clusters 
 and describe the clusters of the cluster group.]

[Explain why this is the best set of options/parameters and clusters.]
